---
title: "DSPM - Assignment 5"
author: 'Submitted by Lukas Günner (Student-ID: 5393972)'
date: "02/10/2021"
output: 
  html_document:
    toc: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Working directory:
# Load project to obtain correct working directory

```
I worked together with Max Haberl (Student ID: 5407084). I hereby assure that my submission is in line with the *Code of Conduct* outlined on the lecture slides.

The working history for this assignment can be accessed via this link:

https://github.com/LukasGuenner/Assignment_5_Guenner.git


## Preparation

Before starting this assignment, I am clearing my workspace and console and then 
loading the packages, necessary to complete this assignment. 
```{r prep, message=FALSE}

rm(list = ls()); cat("\014")

library(tidyverse)
library(naniar)

```

## Getting to know the API

read documentation of the ticketmaster.com API

```{r key, message=F}

# loading API key from separate file 
source("ticketmasterKey.R")

```

Information on the API:

ATTENTION !!!
5000 API calls per day and rate limitation of 5 requests per second!

```{r key, message=F}

# information from the API documentation
root <- "https://app.ticketmaster.com/discovery/v2/"

```




```{r libraries, message=F}

if (!require("jsonlite")) install.packages("jsonlite")
if (!require("httr")) install.packages("httr")
if (!require("rlist")) install.packages("rlist")

library(jsonlite)
library(httr)
library(rlist)

```




```{r key, message=F}



```








